---
title: "Sampling Distribution"
output: learnr::tutorial
runtime: shiny_prerendered

---

```{r setup, include=FALSE}
library(learnr)
library(shiny)
library(tidyverse)
library(plotly)
library(shinyjs)
library(rsconnect)
theme_set(theme_bw())
knitr::opts_chunk$set(echo = FALSE)
```

### Exercise
You need to generate pre-treatment test scores with two different distribution, normal distribution and uniform distribution. Then, compare two sampling distributions of test scores generated with plots.        

For normal distribution, we assume the expectation of the pre-treatment score (E(X)) is 50, the standard deviation of the pre-treatment score is 5, and we sample 1000 times. We also assume the test scores in the uniform distribution runs from 35 to 65.

First, let's generate the sampling distribution of test scores using normal distribution and uniform distribution. Modify the following code to generate the data:
    
        
          
          
          
```{r clt1, exercise=TRUE}
#1. define how many iteration you need to run


#2. create a dataframe to store mean value of each sample


#3. write a loop to generate sampling distribution


#4. write a loop to generate sampling distribution


```

```{r clt1-hint-1}
#1. define how many iteration you need to run
iter<-1000
#2. create a dataframe to store mean value of each sample
rnorm_means <- data.frame(...)
uni_means <- data.frame(...)
#3. write a loop to generate sampling distribution
for (i in 1:iter) {
  #generate a sample using normal distribution
        sample <- rnorm(...)
  #calculate and store the the mean value
        rnorm_means$data[i]  <- ...}
#4. write a loop to generate sampling distribution
for (i in 1:iter) {
  #generate a sample using uniform distribution
  #calculate and store the the mean value
}
```

```{r clt1-hint-2}
#1. define how many iteration you need to run
iter<-1000
#2. create a dataframe to store mean value of each sample
rnorm_means <- data.frame(data = rep(NA, iter))
uni_means <- data.frame(data = rep(NA, iter))
#3. write a loop to generate sampling distribution
for (i in 1:iter) {
  #generate a sample using normal distribution
        sample <- rnorm(n = 100, mean = 50, sd = 5)
  #calculate and store the the mean value
        rnorm_means$data[i]  <- mean(sample)}
#4. write a loop to generate sampling distribution
for (i in 1:iter) {
  #generate a sample using uniform distribution
        sample <- runif(...)
  #calculate and store the the mean value
        }
```


```{r clt1-solution}
#1. define how many iteration you need to run
iter<-1000
#2. create a dataframe to store mean value of each sample
rnorm_means <- data.frame(data = rep(NA, iter))
uni_means <- data.frame(data = rep(NA, iter))
#3. write a loop to generate sampling distribution
for (i in 1:iter) {
  #generate a sample using normal distribution
        sample <- rnorm(n = 100, mean = 50, sd = 5)
  #calculate and store the the mean value
        rnorm_means$data[i]  <- mean(sample)}
#4. write a loop to generate sampling distribution
for (i in 1:iter) {
  #generate a sample using uniform distribution
        sample <- runif(n = 100, min = 35, max = 65)
  #calculate and store the the mean value
        uni_means$data[i]  <- mean(sample)}
```
 
Now, generate the histogram for both sampling distribution. Do you spot any difference?

```{r clt2, exercise=TRUE, exercise.eval=TRUE, exercise.setup ="clt1-solution"}

```

```{r clt2-hint}
#Here is the plot for normal distribution. Please overlay the plot of uniform distribution on top of it
ggplot() + 
geom_histogram(data = rnorm_means, aes(x = data, y = ..density..), bins = 30, alpha = 0.5) +
geom_vline(xintercept = mean(rnorm_means$data), color = 'blue') 
      
```


```{r clt2-solution}
 ggplot() + 
geom_histogram(data = rnorm_means, aes(x = data, y = ..density..), bins = 30, alpha = 0.5) +
geom_vline(xintercept = mean(rnorm_means$data), color = 'blue') + 
geom_histogram(data = uni_means, aes(x = data, y = ..density..), bins = 30, alpha = 0.5,fill = "green") +
geom_vline(xintercept = mean(uni_means$data), color = 'red') 
      
```

```{r}

```

