---
title: "Probability Distribution"
output: learnr::tutorial
runtime: shiny_prerendered

---

```{r setup, include=FALSE}
library(learnr)
library(shiny)
library(tidyverse)
library(plotly)
library(shinyjs)
library(rsconnect)
theme_set(theme_bw())
knitr::opts_chunk$set(echo = FALSE)
```
### Exercise


```{r quiz}
quiz(
  question("Which of following is not an example of continuous variable  :",
    answer("Age of students"),
    answer("Race of students", correct = TRUE),
    answer("Grade of students", correct = TRUE),
    answer("Commute time of students")
  )
)
```

As you have already seen in the last section, we shall assume students' post-treatment scores depend on their pre-treatment scores, regardless of their assigned groups. You shall try to generate pre-treatment scores and post-treatment scores that resembles the dataset you generated previously.

You need to first generate *X*, "pre-treatment score", based on the mean and standard deviation you selected previously in *Illustration for Normal Distribution (Illustration-Probability Distribution)*.Write the code to generate the pre-treatment scores. You shall check the hint if you are unfamiliar with R functions:

```{r dgpx, exercise=TRUE, exercise.eval=TRUE}

```

```{r dgpx-hint}
#use rnorm function; n is number of observations
X<-rnorm(n = 100, mean = ..., sd = ...)
#Check the distribution of X- is it similar to the graph you've seen previously?
hist(X, breaks = 30)

#Store your X for the next step
assign("X", X, envir=globalenv())

```


Now, you shall generate *Y0* and *Y1* that represent the post-treatment scores for our sample of 100 students. Your data should mimic the post-treatment scores you generated previously in *(Conditional Distribution-Probability Distribution)*.       

```{r y, exercise=TRUE, exercise.eval=TRUE, exercise.setup ="dgpx"}

```


```{r y-hint-1}
#Y0 <- beta_0 + beta_1*X + rnorm(N, mean = 0, sd = 1)        


#Y1 <- beta_0 + beta_1*X + tau + rnorm(N, mean = 0, sd = 1)


#Check the distribution of Y0 and Y1- are they similar to the graph you've seen previously?



```


```{r y-hint-2}
#Y0 <- beta_0 + beta_1*X + rnorm(N, mean = 0, sd = 1)        
Y0 <- ... + ...*X + rnorm(100, mean = 0, sd = 1)
#Y1 <- beta_0 + beta_1*X + tau + rnorm(N, mean = 0, sd = 1)
Y1 <- ... + ...*X + ... + rnorm(100, mean = 0, sd = 1)
#Check the distribution of Y0 and Y1- are they similar to the graph you've seen previously?
hist(Y0, breaks = 30)
hist(Y1, breaks = 30)
```


