---
title: "Probability Distribution"
output: learnr::tutorial
runtime: shiny_prerendered

---

```{r setup, include=FALSE}
library(learnr)
library(shiny)
library(tidyverse)
library(plotly)
library(shinyjs)
library(rsconnect)
theme_set(theme_bw())
knitr::opts_chunk$set(echo = FALSE)
```
### Exercise

You need to generate a covariate *frq* that measures how often a student would study for the test on their own in a week. The expected rate of occurrences($lambda$) is 3.       
Please try to generate the covariate using the function rpois(n, lambda), where n is the number of random values to return and lambda is the parameter lambda.

Write the code to generate the covariate. You shall check the hint if you are unfamiliar with R functions:

```{r frq, exercise=TRUE, exercise.eval=TRUE}

```

```{r frq-hint}
frq<-rpois(n= ,lambda =  )
print(frq)
```

```{r frq-solution}
frq<-rpois(n=100,lambda = 3)
print(frq)
```
 
```{r frq-code-check}
grade_code()
```

```{r quiz}
quiz(
  question("Which of following is not an example of continuous variable  :",
    answer("Age of students"),
    answer("Race of students", correct = TRUE),
    answer("Grade of students", correct = TRUE),
    answer("Commute time of students")
  )
)
```

```{r}
rsconnect::deployApp('/Users/tianyangzhou/Desktop/mygithub/Simulation_Shinyapp/Exercise/Exercise-1/Exercise-Probability Distribution.Rmd')
```

